Stimuli Selection

### 2024-10-21 study2/experiment/stimuli_selection/selection.qmd
changes made to scripts

selected_erotic <- c(men, women, homo_men,homo_women)

@@

```{r}
#| code-fold: true
path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/"
path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/"

# Remove all current files
unlink("../stimuli/*")

# Copy each file
for(file in selected) {
  if(str_detect(file, "Male|Female")) {
    file.copy(paste0(path_ero, file), "../stimuli/")
  } else {
    file.copy(paste0(path_naps, file), "../stimuli/")
  }
}
```

>>>>

selected<- c(men, women, homo_men,homo_women)

@@

```{r}
#| code-fold: true
path_ero <- "C:/Users/asf25/OneDrive - University of Sussex/phd/data_base/naps/NAPS_ERO/"

# Remove all current files
unlink("../stimuli/*")
# 
# Copy each file
for (file in selected) {
  file.copy(paste0(path_ero, file), "../stimuli/")
}

```
